Improving content discovery through combining linked data and data mining techniques

### 2016-05-04 report/chapters/07-conclusions.tex
More on conclusions chapter

@@

>>>>

As noted in section~\ref{sec:impact-of-noise}, the fuzzy and noisy nature
of linked data and the semantic web might find an ideal match in the world
of machine learning -- something that an operate on noisy and fuzzy data sets
and still find patterns and insight. That machine learning and data mining
builds upon the idea that data collected might be noisy or incomplete leads
to a strong argument for its application being ideal for the RDF model of
the semantic web.

Statistical methods like machine learning are clearly more tolerant of errors
than more ``hard'' uses such as presenting concrete facts to users based on
embedded semantics or inferring some hierarchical structure for a navigation
feature. Even where the machine learning methods struggle in this particular
research, it does not prevent further research that better tunes the learning
methods used to produce even more useful results.

The question remaining from all of this for the media enterprise, is whether
this combination of semantics and data mining has real application that is
useful.

TODO: Build on survey results

@@

Section~\ref{sec:production-recommendations} covers some recoomedations
for real implementations of semantics for data mining an organisation's
content.

In summary, an organisation can deliver initial value quickly with embedded
semantics (e.g. RDFa) extraction as a general-purpose solution is simple
to implement. The perhaps na\"ive mapping presented in this research for
converting RDF to feature sets performs well enough if the gaps and noise
in the data have a tolerable effect on the outcomes.

Media organisations can iterate very quickly on this simple idea and find
approaches that work for them and at each iteration consider the following:

\begin{itemize}
\item Can we implement entity extraction to supplement the embedded semantics?
\item How do we best tune any entity extaction over time?
\end{itemize}
